SODA POP : Robust online Partial Ordering Planning for real life applications

### 2015-11-19 article/article.tex
new gitignore + redaction + examples

\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\usepackage[usenames,dvipsnames]{color}
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={Antoine GRÉA Samir AKNINE Laetitia MATIGNON},
            pdftitle={SODA POP : Robust online Partial Ordering Planning for real life applications},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{listings}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}

@@

\begin{document}
\maketitle
\begin{abstract}
This is the best of all abstracts ever !

It consists of two paragraphs but that is more than enough for it to be
awesome.
\end{abstract}

@@

These problems call for new ways to improve the answer and behavior of a
planner. These improvements must provide relevant plan information
pointing out exactly what needs to be done in order to make a planning
problem solvable, even in the case of obviously broken input data. We
aim to solve this in this paper while preserving the advantages of PSP
algorithms (flexibly, easy fixing of plans, soudness and
completeness)\textgreater{}. Our Soft Ordering and Defect Aware Partial
Ordering Planning (SODA POP) algorithm will target those issues.

@@

All these issues are caused by what we call \emph{defects} as they are
not regular PSP flaws but they still cause problems with execution and
results. We will address these defects and propose a way to fix them in
\hyperref[defects]{the next section}.

@@

@@

\hyperdef{}{defects}{\subsection{Defect resolution}\label{defects}}

@@

This auxiliary algorithm is meant to deal with failure. It will heal the
plan to make the failure recoverable for the next iteration of POP. Of
course it can't fix the plan by keeping the problem as it is. This
obviously breaks some properties as the algorithm no longer adheres to
the specification of the input, but in exchange it will always issue a
valid plan whatever happens. For more information on this property go
take a look at the \hyperref[hypersoundness]{appropriate section
bellow}.

@@

\Function{soda}{Problem $P$} \State \(P.p \gets\)
\Call{properPlan}{$P.G$, $P.A$} \State \Call{clean}{$P$} \State bool
\(valid \gets false\) \While{$\lnot valid$} \(valid \gets\)
\State \Call{pop}{$P$} \(= Success\) \If{$valid$}
\State \Call{clean}{$P$} \State \Return \(Success\) \EndIf
        \State \Call{heal}{$P$} \EndWhile
\EndFunction

@@

\hyperdef{}{ref-weldux5fintroductionux5f1994}{\label{ref-weldux5fintroductionux5f1994}}
{[}1{]} D. S. Weld, ``An introduction to least commitment planning,''
\emph{AI magazine}, vol. 15, no. 4, p. 27, 1994.

\hyperdef{}{ref-richterux5flamaux5f2011}{\label{ref-richterux5flamaux5f2011}}
{[}2{]} S. Richter, M. Westphal, and M. Helmert, ``LAMA 2008 and 2011,''
in \emph{International Planning Competition}, 2011, pp. 117--124.

\hyperdef{}{ref-ghallabux5fautomatedux5f2004}{\label{ref-ghallabux5fautomatedux5f2004}}
{[}3{]} M. Ghallab, D. S. Nau, and P. Traverso, \emph{Automated
planning: theory and practice}. Amsterdam ; Boston: Elsevier/Morgan
Kaufmann, 2004.

\hyperdef{}{ref-vanux5fderux5fkrogtux5fplanux5f2005}{\label{ref-vanux5fderux5fkrogtux5fplanux5f2005}}
{[}4{]} R. Van Der Krogt and M. De Weerdt, ``Plan Repair as an Extension
of Planning.'' in \emph{ICAPS}, 2005, vol. 5, pp. 161--170.

\hyperdef{}{ref-erolux5fumcp:ux5f1994}{\label{ref-erolux5fumcp:ux5f1994}}
{[}5{]} K. Erol, J. A. Hendler, and D. S. Nau, ``UMCP: A Sound and
Complete Procedure for Hierarchical Task-network Planning.'' in
\emph{AIPS}, 1994, vol. 94, pp. 249--254.

\hyperdef{}{ref-penberthyux5fucpop:ux5f1992}{\label{ref-penberthyux5fucpop:ux5f1992}}
{[}6{]} J. S. Penberthy, D. S. Weld, and others, ``UCPOP: A Sound,
Complete, Partial Order Planner for ADL.'' \emph{Kr}, vol. 92, pp.
103--114, 1992.

\hyperdef{}{ref-bechonux5fhipop:ux5f2014}{\label{ref-bechonux5fhipop:ux5f2014}}
{[}7{]} P. Bechon, M. Barbier, G. Infantes, C. Lesire, and V. Vidal,
``HiPOP: Hierarchical Partial-Order Planning,'' in \emph{STAIRS 2014:
Proceedings of the 7th European Starting AI Researcher Symposium}, 2014,
vol. 264, p. 51.

\hyperdef{}{ref-garciaux5fdefeasibleux5f2008}{\label{ref-garciaux5fdefeasibleux5f2008}}
{[}8{]} D. R. García, A. J. García, and G. R. Simari, ``Defeasible
reasoning and partial order planning,'' in \emph{Foundations of
Information and Knowledge Systems}, Springer, 2008, pp. 311--328.

\hyperdef{}{ref-colesux5fforward-chainingux5f2010}{\label{ref-colesux5fforward-chainingux5f2010}}
{[}9{]} A. J. Coles, A. Coles, M. Fox, and D. Long, ``Forward-Chaining
Partial-Order Planning.'' in \emph{ICAPS}, 2010, pp. 42--49.

>>>>

\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{hyperref}
\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref
\hypersetup{unicode=true,
            pdftitle={SODA POP : Robust online Partial Ordering Planning for real life applications},
            pdfauthor={Antoine GRÉA Samir AKNINE Laetitia MATIGNON},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{listings}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}

@@

\begin{document}
\maketitle
\begin{abstract}
In cognitive applications the needs of ordering action to reach a goal
created the dommain of automated planning. This domain is actually
domined by researches arround performance and the advances in state
based planning has eclipsed other less efficient ways of doing. Partial
Ordering Planning (POP) is one of the most flexible way to order actions
and create plan that can be refined easily. This can be used to achieve
greater resilience, repairing capabilities and soft resolution that
applications like online plan recognision or decision making can benefit
from. This calls for new solutions that our set of algorithm named Soft
Ordering and Defect Aware Partial Ordering Planning (SODA POP) targets
with plan quality in mind. The algorithm seeks a new set of defects in
broken input and actions in order to fix them and even to derive the
problem in order to always output a valid plan in case the problem is
imposible to solve.
\end{abstract}

@@

These problems call for new ways to improve the answer and behavior of a
planner. These improvements must provide relevant plan information
pointing out exactly what needs to be done in order to make a planning
problem solvable, even in the case of obviously broken input data. We
aim to solve this in this paper while preserving the advantages of PSP
algorithms (flexibly, easy fixing of plans, soudness and completeness).
Our Soft Ordering and Defect Aware Partial Ordering Planning (SODA POP)
algorithm will target those issues.

@@

All these issues are caused by what we call \emph{defects} as they are
not regular PSP flaws but they still cause problems with execution and
results. We will address these defects and propose a way to fix them in
\protect\hyperlink{defects}{the next section}.

@@

On our example it illustrate really well the need for resilience. The
algorithm simply recursively chose the actions and end up with the
partial plan represented in figure \ref{fig:proper}. The partial plan
doesn't have an initial state (because of its offline nature). This plan
also shows several cycles and obvious problems. Moreover the plan has
all the steps of the correct final plan and therefore remove the subgoal
search in POP if it uses this plan has input (after it has been cleaned
obviously).

\begin{figure}[htbp]
\centering
\includegraphics{graphics/proper.pdf}
\caption{Proper plan of the example goal\label{fig:proper}}
\end{figure}

@@

\hypertarget{defects}{\subsection{Defect resolution}\label{defects}}

@@

This auxiliary algorithm is meant to deal with failure. It will heal the
plan to make the failure recoverable for the next iteration of POP. Of
course it can't fix the plan by keeping the problem as it is. This
obviously breaks some properties as the algorithm no longer adheres to
the specification of the input, but in exchange it will always issue a
valid plan whatever happens. For more information on this property go
take a look at the \protect\hyperlink{hypersoundness}{appropriate
section bellow}.

@@

\Function{soda}{Problem $P$} \State \(P.p \gets\)
\Call{properPlan}{$P.G$, $P.A$} \State \Call{clean}{$P$} \State bool
\(valid \gets false\) \While{$\lnot valid$} \State \(valid \gets\)
\Call{pop}{$P$} \(= Success\) \If{$valid$} \State \Call{clean}{$P$}
\State \Return \(Success\) \EndIf
        \State \Call{heal}{$P$} \EndWhile
\EndFunction

@@

\hypertarget{refs}{}
\hypertarget{ref-weldux5fintroductionux5f1994}{}
{[}1{]} D. S. Weld, ``An introduction to least commitment planning,''
\emph{AI magazine}, vol. 15, no. 4, p. 27, 1994.

\hypertarget{ref-richterux5flamaux5f2011}{}
{[}2{]} S. Richter, M. Westphal, and M. Helmert, ``LAMA 2008 and 2011,''
in \emph{International Planning Competition}, 2011, pp. 117--124.

\hypertarget{ref-ghallabux5fautomatedux5f2004}{}
{[}3{]} M. Ghallab, D. S. Nau, and P. Traverso, \emph{Automated
planning: theory and practice}. Amsterdam ; Boston: Elsevier/Morgan
Kaufmann, 2004.

\hypertarget{ref-vanux5fderux5fkrogtux5fplanux5f2005}{}
{[}4{]} R. Van Der Krogt and M. De Weerdt, ``Plan Repair as an Extension
of Planning.'' in \emph{ICAPS}, 2005, vol. 5, pp. 161--170.

\hypertarget{ref-erolux5fumcp:ux5f1994}{}
{[}5{]} K. Erol, J. A. Hendler, and D. S. Nau, ``UMCP: A Sound and
Complete Procedure for Hierarchical Task-network Planning.'' in
\emph{AIPS}, 1994, vol. 94, pp. 249--254.

\hypertarget{ref-penberthyux5fucpop:ux5f1992}{}
{[}6{]} J. S. Penberthy, D. S. Weld, and others, ``UCPOP: A Sound,
Complete, Partial Order Planner for ADL.'' \emph{Kr}, vol. 92, pp.
103--114, 1992.

\hypertarget{ref-bechonux5fhipop:ux5f2014}{}
{[}7{]} P. Bechon, M. Barbier, G. Infantes, C. Lesire, and V. Vidal,
``HiPOP: Hierarchical Partial-Order Planning,'' in \emph{STAIRS 2014:
Proceedings of the 7th European Starting AI Researcher Symposium}, 2014,
vol. 264, p. 51.

\hypertarget{ref-garciaux5fdefeasibleux5f2008}{}
{[}8{]} D. R. García, A. J. García, and G. R. Simari, ``Defeasible
reasoning and partial order planning,'' in \emph{Foundations of
Information and Knowledge Systems}, Springer, 2008, pp. 311--328.

\hypertarget{ref-colesux5fforward-chainingux5f2010}{}
{[}9{]} A. J. Coles, A. Coles, M. Fox, and D. Long, ``Forward-Chaining
Partial-Order Planning.'' in \emph{ICAPS}, 2010, pp. 42--49.
